\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{soul}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.8]{fdsymbol}
\usepackage{ragged2e}
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\definecolor{TuftsBlue}{RGB}{62, 142, 222}
\definecolor{ImperialBlue}{RGB}{0, 62, 116}

%-----------Sections-Formatting----------------- 
\titleformat{\section}{\vspace{-8pt}\bf\scshape\raggedright\Large\color{TuftsBlue}
}{}{0em}{}[\vspace{-3pt}\color{TuftsBlue}\titlerule\vspace{-5pt}]

%-----------Custom-Commands-definition----------------- 

% Summary
\newcommand{\SummaryRole}[4]{
  \vspace{0pt}\item[]
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\NoHeadRole}[2]{
  \vspace{-5pt}\item[]
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textit{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}


\newcommand{\RoleII}[4]{
  \vspace{0pt}\item[]
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\HeadTypeI}[2]{ %Heading for Employment roll project 
  \vspace{-2pt}\item[]
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1}{\small{\textit{#2}}} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\HeadTypeII}[3]{
  \vspace{-2pt}\item[]
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1}&{\small{\textit{#2}}} \\
    {#3}
    \end{tabular*}\vspace{-8pt}
}


\newcommand{\BulletTypeSummary}[1]
{\item\small\justifying{{\hspace{-3pt}#1\vspace{-6pt}}}}

\newcommand{\BulletI}[1]
{\item\small\justifying{{\hspace{0pt}#1\vspace{-1pt}}}}

\newcommand{\BulletII}[2]
{\item\small{\justifying\textbf{#1}\justifying{:#2\vspace{-1pt}}}}

\newcommand{\BulletIII}[2]
{\item\small{\textbf{#1}{#2 \vspace{-7.5pt}}}}

\newcommand{\BulletIV}[2] % Bullet 
{\item\small{{#1}{#2 \vspace{-7.5pt}}}}

%-----------List-Bullit-definition----------------- 
\renewcommand{\labelitemi}{$\medblacksquare$}
\renewcommand{\labelitemii}{$\smallblacksquare$}
\renewcommand{\labelitemiii}{$\smallblacksquare$}

%-----------List-Environment-definition----------------- 
\newcommand{\BeginList}{\begin{itemize}[leftmargin=0.00in]}
\newcommand{\EndList}{\end{itemize}\vspace{-5pt}}

\newcommand{\BeginListII}{\begin{itemize}[leftmargin=0.15in]} 
\newcommand{\EndListII}{\end{itemize}\vspace{-5pt}}
%no hspace list

\newcommand{\BeginSubList}{\begin{itemize}[leftmargin=0.25in]}
\newcommand{\EndSubList}{\end{itemize}\vspace{-8pt}}


%-----------Resume-Start----------------- 

\begin{document}

%----------HEADING-----------------
\begin{center}
{\Huge{\bf\scshape{HAOTIAN JIA}}} \vspace{5pt} \\
{
\href{tel:18577565263}{\faPhoneSquare~\underline{\smash{+1 857-756-5263}}}\quad
{\href{mailto:haotian.jia@tufts.edu}{\faEnvelope~\underline{\smash{haotian.jia@tufts.edu}}}}\quad
\href{https://www.linkedin.com/in/haotianjia}{\faLinkedin~\underline{\smash{{linkedIn}}}}\quad
{\faBuilding~Medford, MA, 02155}}
    \vspace{0pt}
\end{center}


%-----------SUMMARY-----------------
\section{Summary}
\BeginListII
% \BulletTypeSummary{Target position: thermal enginner}

\BulletTypeSummary{PhD candidate in Mechanical Engineering with a focus on Heat Transfer, Fluid Mechanics, and Mass Transfer, expertise in analytical problem-solving with a profound understanding of the fundamental physics associated with these fields.}

\BulletTypeSummary{5+ years of professional experience in scientific research, proficiency in data processing, visualization, and analysis.}  
% in mechanical design, prototyping, and testing foe experimental resueasrch.}

\BulletTypeSummary{Proficient in presenting reports and information; Experienced in working in team-based environments, collaborating effectively, and possessing strong communication skills in English and Mandarin. }

% \BulletTypeSummary{Mechanical Design, Prototyping \& Testing Modeling, Simulation \& Theoretical Research}

% \BulletIII{English Communication Skills~|~}{Successfully delivered several presentations and collaborated with multi-disciplinary teams and industry partners in STTR (Small Business Technology Transfer) projects for early-stage research, development, and deployment initiatives.}

\EndListII


%-----------EDUCATION-----------------
\section{Education}
\BeginList
    \Role
      {Tufts University}{Medford, MA}
      {PhD Mechanical Engineering \footnotesize{(GPA: 3.82/4.0)}}{Sep 2020 -- Present}
    \NoHeadRole
      {MS Mechanical Engineering}{Sep 2018 -- Present}
    \Role
      {Beijing Forestry University}{Beijing, China}
      {BS Mechanical Design, Manufacturing, and Automation}{Sep 2014 -- Jun 2018}
\EndList

  
%-----------EMPLOYMENT-----------------
\section{Employment}      
\BeginList
\RoleII
{Department of Mechanical Engineering, Tufts University}{Medford, MA}
{Research Assistant}{Sep 2019 -- Present}
\BeginListII
\HeadTypeI{Permeability measurement of aerogel~|~}{funded by NSF award 153060}
      \BeginList
      \BulletI{Designed, constructed, and tested an experimental apparatus to precisely measure aerogel permeability through two independent methods. The apparatus utilized CO$_2$ under pressures up to 1850 PSI and temperatures of 50°C.}

      \BulletI{Improved the existing experimental method for direct permeability measurement and developed a non-destructive aerogel permeability testing method using Duhamel's theorem.}   
      \BulletI{Developed several custom programs using LabVIEW and MATLAB for data collection and post-processing, respectively.}
      % \BulletI{Developed a data acquisition and post-processing system using National Instruments LabVIEW and hardware.
      \EndList

\HeadTypeI{Jet-impingement enhanced freeze drying~|~}{funded by NSF STTR Phase I award 2014881}
      \BeginList
      \BulletI{Optimized Collaborator's (Aerogel Technologies, LLC.) patented aerogel freeze-drying process by designing, constructing, commissioning, and utilizing a first-of-its-kind drying system demo, resulting in a 75\% reduction in production time.}
      \BulletI{Developed dehumidification process for compressed air flow, achieving a dew point as low as -40°C while maintaining a high mass flow rate of up to 12.7 SCFM.}
      \EndList
      
\HeadTypeI{Microchannel fabrication~|~}{Funded by NSF award 2140033 (Ongoing)}
      \BeginList
      \BulletI{Designed and fabricated PDMS microchannel with complex sidewall geometry using the method of SU-8 Soft-lithography in Tufts Micro and Nano Fabrication Facility (class 1000 cleanroom). conducted several Preliminary Experiments using micro-PIV.}
      % \BulletI{}
      \EndList
      
\EndListII

\RoleII
{Department of Mathematics, Imperial College London}{London, UK}
{Research Assistant, Global Research Assistant Program (GRAP)}{Jun 2022 -- Aug 2022}
\BeginListII
\HeadTypeI{Inertial Effects on the Flow Resistance of Axial Groove Heat Pipes}{}
      \BeginList
      \BulletI{Improved an 
      which simplifies a 3-dimensional 2-phase flow problem into 2D several 2D 
      Modeled and solved the partial differential equations governing 2-phase flow by employing asymptotic expansion techniques and}
      utilizing MATLAB finite element method solvers.
      \EndList

\HeadTypeI{Enhanced Lubrication and Pumping of Flow in Superhydrophobic Microchannels}{}
      \BeginList
      \BulletI{Improved the modeling of mass transfer for photo-surfactants seeded flow in a microchannel with a textured surface, surface tension and verified the photo chemistry behaviousr of photo-surfactants underego UV and Blue light transitions.}
      \EndList
\EndListII

\EndList

%-----------Relevant Courses-----------------
\section{Relevant Courses}
\BeginListII
\BulletIII{Transport Phenomena~|~}{Fluid Mechanics, Thermal-fluid Transport, Microfluidics, heat transfer, High Reynolds Number Flow, Analytic Transport Phenomena, Thermal Management Of Electronics}
\BulletIII{Numerical Modeling~|~}{Applied Mathematics for Engineers, Numerical Analysis, Simulation for Mechanical Engineer}
\BulletIII{Transport Phenomena~|~}{Fluid Mechanics, Thermal-fluid Transport, Microfluidics, heat transfer, High Reynolds Number Flow, Analytic Transport Phenomena, Thermal Management Of Electronics}
\BulletIII{Numerical Modeling~|~}{Applied Mathematics for Engineers, Numerical Analysis, Simulation for Mechanical Engineer}
\EndListII

%-----------PROJECTS-----------------

\section{Project}
\BeginList
\HeadTypeI{2 Degree-of-Freedom Planar Robot Arm Design \& Control}{}
      \BeginSubList
      \BulletI{Customized a National Instruments myRIO using the LabVIEW FPGA Module to design and compare multiple control methods for a 2-degree-of-freedom planar robot arm.}
      \EndSubList
      
\HeadTypeI{Solution for Cerebral Palsy Patient to Eat Independently}{}
      \BeginSubList
      \BulletI{Collaborated with patients and caregivers to design and fabricate a rotary food supply mechanism using LEGO and an Arduino-controlled stepper motor, while collaborating with teammates to deliver a preliminary solution.}
      \EndSubList
      
\HeadTypeI{Website Development for Transport Phenomena Lab}{}
      \BeginSubList
      \BulletI{Developed and currently maintain the research group site on WordPress, see \href{https://sites.tufts.edu/tplab/}{\underline{\smash{https://sites.tufts.edu/tplab}}} for reference.}
      \EndSubList

\EndList


      


% \EndList



%-----------SKILLS-----------------
\section{Technical Skills}
\BeginList    
    
    \BulletIII{Heat Transfer and Fluid Flow Modeling | }{Expertise in conduction, forced convection, high Reynolds number flow, microfluidics, and thermal management for electronics. Experienced in modeling for heat sinks, heat pipes, fans, impinging jets, heat exchangers, etc.}

    \BulletIII{Numerical Modeling, Simulation \& Analysis | }{ Proficient in numerical analysis tools, applying Finite Element Method (FEM/FEA) and skilled in designing custom numerical solvers. Proficient using the \underline{\smash{MATLAB Partial Differential Equation Toolbox}}. Computational Fluid Dynamics, Proficient in using Computational Fluid Dynamics tools (\underline{\smash{Ansys Fluent}} and \underline{COMSOL})}
    
    \BulletIII{Mechanical Design \& Manufacturing | }{8+ years of experience utilizing 2D \& 3D CAD software (\underline{SolidWorks}, \underline{\smash{Solid Edge}}, \underline{AutoCAD}). Expertise in various manufacturing methods and experience in \underline{G-code} and \underline{MasterCAM} for CNC manufacturing.} % Computer Numerical Control (CNC) 

    \BulletIII{Experimental Data Acquisition | }{Developed multiple test and measurement systems utilizing National Instrument hardware (\underline{\smash{NI-DAQ}}) within the \underline{LabVIEW} environment to collect and preprocess data. Expertise in measurement techniques for fluid flow (vortex, micro-PIV) and heat transfer with proficiency in error analysis.}

    \BulletIII{Data Processing, \& analysis | }{5+ years of experience using using \underline{MATLAB} processing and visualizing scientific data, using \underline{Excel} and. Proficient in utilizing illustrative post-processing techniques to support project presentation via \underline{Inkscape} and \underline{PowerPoint} }
    
    \BulletIII{Document Drafting \& Academic writing | }{Proficient in utilizing \underline{Microsoft Word} and \underline{LaTeX} for drafting project summaries, proposals, data management plans, and other documents related to scientific research.}



\EndList

      
      % {MATLAB, LaTeX, SolidWorks, Inkscape, LabVIEW, Microsoft Office, Ansys Fluent(CFD)}
    % \BulletIII{Experienced}
    %   {Adobe Illustrator, COMSOL, WordPress, Arduino, High-performance computing (HPC) environment}
    % \BulletIII{Basic Knowledge}
    %   {HTML, CSS, JavaScript, C, Assembly Language, Mathematica, G-code}
%-----------EXPERIENCE-----------------
\section{Leadership \& Collaboration Experience}
\BeginList

\Role
{PR Department, Association Federation of Beijing Forestry University}
{Beijing, China}
{Vice Minister}
{Jul 2015 -- Sep 2016}
  \BeginSubList
  \BulletI{Represented the university and its students in a diverse range of events organized by other universities in the Beijing area, fostering collaboration and networking opportunities.}
  \EndSubList
  
\Role
{LvFangCheng Electroacoustic Club, Art Troupe of Beijing Forestry University}
{Beijing, China}
{President}
{Nov 2016 -- Nov 2017}
    \BeginSubList
    \BulletI{Coordinated with performance venues, organized several music events to provide opportunities for student performers.}
    \BulletI{Oversaw the management of the club, including recruitment, rehearsals, and scheduling of performances.}
    \EndSubList
    
% \Role
% {APHASIA \small{(Post-rock Band, Non-professional)}}
% {Beijing, China}
% {Rhythm Guitar}
% {Nov 2015 -- May 2017}


\EndList

%-----------EXPERIENCE-----------------
\section{Publications}
\BeginList
\BulletIV{Jia, H., Hodes, M., and  Kirk, T., "Inertial Effects on the Adiabatic-Section Flow Resistance of Axial Groove Heat Pipes." In progress for submission to the \textit{Journal of Fluid Mechanics}.}

\BulletIV{Mayer, M., Jia, H., Adler, J., Hu, X., and Hodes, M., "Enhanced Lubrication and Pumping of Flow in Superhydrophobic Microchannels via Chromocapillarity." In progress for submission to the \textit{Journal of Fluid Mechanics}.}

\BulletIV{Jia, H., Dinh, H., Hodes, M., Griffin, J., Mayer, M., Diorio, M., and Karamanis, G., "An Apparatus to Measure Permeability of Aerogels by Redundant Methods." In progress for submission.}

\BulletIV{Jia, H., Karamanis, G., Abolorunke, F., Dinh, H., Griffin, J., and Hodes, M., "Jet-Impingement-Enhanced Ambient-Pressure Freeze Drying Of Aerogels." In progress for submission.}


\EndList
%-----------EXPERIENCE-----------------
\section{Conference Talks \& Presentations}
\BeginList
\BulletIII{10th International Congress on
Industrial and Applied Mathematics (2023)~|~}{Presented a minisymposia talk titled \textit{"Inertial Effects on the Adiabatic-Section Flow Resistance of Axial Groove Heat Pipes"}}

\BulletIII{The Red Lotus Project~|~}{Presented a series of talks at video-conference events and mini-symposia to mathematicians at Imperial College London, promoting interdisciplinary collaboration in the field of surface engineering, with a focus on microfabrication and photochemistry applications.}

\BulletIII{Online Aerogel Seminar 2020~|~}{Presented a talk titled \textit{"Permeability of Aerogels under Supercritical CO$_2$ Conditions"}}

\BulletIII{Tufts International Center 2019 Workshop~|~}{Participated in \textit{"Transitioning to Graduate School"}, a panel discussion.}

\EndList



%-------------------------------------------
\end{document}